%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
\documentclass[]{resume_en}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shuhao}{Wang}{(+86)15210561025 | \urlstyle{same}\href{
mailto:shudiwsh2009@gmail.com}{shudiwsh2009@gmail.com}\\
Room 11-419, East Main Building, IISE lab, Tsinghua University, Haidian, Beijing
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Tsinghua University}
\descript{School of Software\\MEng in Software Engineering}
\location{Sep 2013 - Jul 2016 | Beijing}
The Institute of Information System \& Engineering\\
{\bf Research Area:} Business Process Management - Behavioral similarity measure and evaluation on process models
\sectionsep

\subsection{Tsinghua University}
\descript{School of Software\\BS in Computer Software}
\location{Sep 2009 - Jul 2016 | Beijing}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/shudiwsh2009}{\bf Shudi Wang} \\
LinkedIn://  \href{https://cn.linkedin.com/in/wangshuhao}{\bf wangshuhao} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Introduction to Algorithms\\
Workflow Technology\\
Data Quality\\
Software Project Management\\
Requirements Engineering\\
Machine Learning \& Knowledge Discovery\\
Data Warehousing and Data Mining\\
\sectionsep

\subsection{Undergraduate}
Information Retrieval \\
Operating Systems \\
Principles of Database System \\
Compilers \\
Artificial Intelligence \\
Principles of Computer Organization \\
Computer Networks \\
Assembly Language Programming \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
2015~~~National Scholarship
2014~~~Tsinghua - Glodon First Scholarship
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{} Go \textbullet{} Python \textbullet{} \LaTeX\ \\
React \textbullet{} HTML5\\
MongoDB \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{CreditEase\\Big Data Innovation Center}
\descript{| Backend R\&D Intern}
\location{Jun 2015 - Sep 2015 | Beijing, China}
\vspace{\topsep}
\begin{tightemize}
\item Technique: React, Go, MySQL
\item In charge of the development of H5 purchasing website and WeChat open platform of a financial product, which brings over 10 millions of trading volume (via H5 website) since published online.
\item Major contribution to the project: significant pages and modules such as the process of first purchase and following purchases, pages of assets and coupons, binding between financial account and WeChat, person account management.
\end{tightemize}
\shortsectionsep

\runsubsection{Beijing Baijugu Technology Co., ltd.}
\descript{| Co-founder, Software Engineer}
\location{Apr 2014 - Jan 2015 | Beijing, China}
\begin{tightemize}
\item Implementation of epibolic websites, mobile app servers, WeChat open platform, EDM systems, etc.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Process Data Space}
\descript{| Foundation Project}
\location{Dec 2013 - Jan 2015 | Beijing, China | Techinical Team Leader}
\begin{tightemize}
\item Giving instructions to 5 undergradutes and help with their graduation projects.
\item Design and build the structure of the system.
\item Design and implement the modules of model management and model analyzer.
\end{tightemize}
\shortsectionsep

\runsubsection{Reservation System for Center of Student Learning and Development}
\descript{| Campus Website}
\location{Apr 2015 - Sep 2015 | Beijing, China | Development Leader}
\begin{tightemize}
\item Development of the frontend and backend of the reservation system.
\item Manage tens of teachers and hunderds of reservation records per week.
\end{tightemize}
\shortsectionsep

\runsubsection{Marketing Solutions for ANSYS China}
\descript{| Enterprise Apps}
\location{Apr 2014 - Jan 2015 | Beijing, China | Software Engineer}
\begin{tightemize}
\item Update and maintainence of the official website of ANSYS China.
\item Implementation of the WeChat open platform, whose amount of subscribers increases by 6 times in the first 6 months.
\end{tightemize}
\shortsectionsep

\runsubsection{BeehiveZ}
\descript{| Research Project}
\location{Sep 2013 - Present | Beijing, China | Software Engineer}
\begin{tightemize}
\item Design and implement process model behaviroal similarity measure algorithms - SSDT \& TAGER.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -1.6cm} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
